KV Analysis for Non-Expressive performances

### 2021-02-01 material/expstimuli/analysis/stim_n/duration.Rmd
update comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Description: This is a rough overview of non-expressive performance (Duration) from teaching-v2.0.

@@

### Valid performances (exclude outliers)
```{r outlier, echo = FALSE}
excluded_duration <- duration[Mean < duration_all$Mean+3*duration_all$SD & Mean > duration_all$Mean-3*duration_all$SD]
print(excluded_duration)
```
- The number of excluded performance: `r duration_all$N-nrow(excluded_duration)`

@@

### Valid performances (exclude outliers)
```{r cv_outlier, echo = FALSE}
excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```
- The number of excluded performance: `r cv_all$N-nrow(excluded_cv)`

>>>>

Description: This is a rough overview of non-expressive performance (Duration) from [music-teaching (experiment2)](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-2).

Non-expressive performances: data from practice trials

@@

# Valid performances (exclude Duration outliers)
- Exclude mean Duration outside 3SD

```{r outlier, echo = FALSE}
excluded_duration <- duration[Mean < duration_all$Mean+3*duration_all$SD & Mean > duration_all$Mean-3*duration_all$SD]
print(excluded_duration)
```
- The number of excluded performance: `r duration_all$N-nrow(excluded_duration)`

@@

# Valid performances (exclude CVs outliers)
- Exclude mean CVs outside 3SD

```{r cv_outlier, echo = FALSE}
excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```
- The number of excluded performance: `r cv_all$N-nrow(excluded_cv)`

### 2021-02-01 material/expstimuli/analysis/stim_n/ioi_offset.Rmd
update comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Description: This is a rough overview of non-expressive performance (IOI-offset) from teaching-v2.0.

@@

### Valid performances (exclude outliers)
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```
- The number of excluded performance: `r ioi_all$N-nrow(excluded_ioi)`

@@

### Valid performances (exclude outliers)
```{r cv_outlier, echo = FALSE}
excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```
- The number of excluded performance: `r cv_all$N-nrow(excluded_cv)`

>>>>

Description: This is a rough overview of non-expressive performance (IOI-Offset) from [music-teaching (experiment2)](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-2).

Non-expressive performances: data from practice trials

@@

# Valid performances (exclude outliers)
- Exclude mean IOIs outside 3SD

```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```
- The number of excluded performance: `r ioi_all$N-nrow(excluded_ioi)`

@@

# Valid performances (exclude outliers)
- Exclude mean CVs outside 3SD

```{r cv_outlier, echo = FALSE}
excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```
- The number of excluded performance: `r cv_all$N-nrow(excluded_cv)`

### 2021-02-01 material/expstimuli/analysis/stim_n/ioi_onset.Rmd
update comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Description: This is a rough overview of non-expressive performance (IOI-Onset) from teaching-v2.0.

@@

### Valid performances (exclude outliers)
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```
- The number of excluded performance: `r ioi_all$N-nrow(excluded_ioi)`

>>>>

Description: This is a rough overview of non-expressive performance (IOI-Onset) from [music-teaching (experiment2)](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-2).

Non-expressive performances: data from practice trials

@@

# Valid performances (exclude IOIs outliers)
- Exclude mean IOIs outside 3SD

```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```
- The number of excluded performance: `r ioi_all$N-nrow(excluded_ioi)`

### 2021-02-01 material/expstimuli/analysis/stim_n/kv.Rmd
update comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Description: This is a rough overview of non-expressive performance (KV) from teaching-v2.0.

@@

### Valid performances (exclude outliers)
```{r outlier, echo = FALSE}
excluded_kv <- kv[Mean < kv_all$Mean+3*kv_all$SD & Mean > kv_all$Mean-3*kv_all$SD]
print(excluded_kv)
```
- The number of excluded performance: `r kv_all$N-nrow(excluded_kv)`

>>>>

Description: This is a rough overview of non-expressive performance (KV) from [music-teaching (experiment2)](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-2).

Non-expressive performances: data from practice trials

@@

# Valid performances (exclude KVs outliers)
- Exclude mean KVs outside 3SD

```{r outlier, echo = FALSE}
excluded_kv <- kv[Mean < kv_all$Mean+3*kv_all$SD & Mean > kv_all$Mean-3*kv_all$SD]
print(excluded_kv)
```
- The number of excluded performance: `r kv_all$N-nrow(excluded_kv)`
